Polls of polls to predict the 2024 election

### 2024-11-05 paper/paper.qmd
updating date of data

Our polling data analysis was conducted using the R programming language [@citeR]. The dataset, sourced from FiveThirtyEight [@fivethirtyeight2024] and encompassing polling data up to November 2, 2024, provides a comprehensive snapshot of public opinion leading into the election. Following the guidelines in @tellingstories, we examined factors affecting voter support percentages, such as poll timing, polling organization characteristics, and regional differences.

>>>>

Our polling data analysis was conducted using the R programming language [@citeR]. The dataset, sourced from FiveThirtyEight [@fivethirtyeight2024] and encompassing polling data up to October 21, 2024, provides a comprehensive snapshot of public opinion leading into the election. Following the guidelines in @tellingstories, we examined factors affecting voter support percentages, such as poll timing, polling organization characteristics, and regional differences.
